---
title: "TidyTemplate"
date: 2020-11-27
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(widyr)
library(ggraph)
library(igraph)
library(tidygraph)
library(emo)
library(emojifont)
library(here)
library(extrafont)
library(extrafontdb)
library(cowplot)
library(showtext)
library(showtextdb)
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

hike <- readr::read_rds(url('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-24/hike_data.rds'))

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
hike <- tt$hike_data

hike %>% 
  count(name,sort=TRUE)

hike_2 <- hike %>% 
  separate(length,into = c("length","type"),sep = ",") %>% 
  mutate(length=parse_number(length),
         type=str_squish(type),
         length_num=case_when(type=="one-way"~length,
                          type=="roundtrip"~length/2,
                          TRUE ~ length)) %>% 
  relocate(name,location,length,type,length_num)
  
#Find all the hikes with no dog mention in features
hike_2$name[!str_detect(hike_2$features,"Dogs" )]

#Dog Friendly/unfriendly Hikes
hike_3 <- hike_2 %>% 
  mutate(seq=1:n()) %>% 
  unnest(features) %>% 
  group_by(name) %>% 
  mutate(dogs_allowed=case_when(features=="Dogs allowed on leash"~"Dogs allowed",
                                features=="Dogs not allowed"~"Dogs not allowed",
                                TRUE ~ NA_character_)) %>% 
  relocate(dogs_allowed) %>% 
  fill(.,dogs_allowed,.direction="downup") %>% 
  mutate(dogs_allowed=replace_na(dogs_allowed,"Not mentioned")) %>% 
  relocate(seq) %>% 
  ungroup() %>% 
  mutate(rating_num=parse_number(rating))
```


#Correlation

```{r}
`%nin%` = Negate(`%in%`)

#What are dog friendly/unfriendly hike most correlated to

cor_pair <- hike_3 %>% 
  count(name,seq,features) %>% 
  pairwise_cor(features,seq,n) %>% 
  arrange(desc(correlation))

#Filtering out correlation with Dogs either allowed/not allowed
dogs_cor <- cor_pair %>% 
  filter(str_detect(item1,"Dogs"))  %>% 
  rename("features"=item2) %>% 
  mutate(item1=case_when(item1=="Dogs allowed on leash"~"Dogs allowed",
                         TRUE~item1)) %>% 
  filter(features %nin% c("Dogs allowed on leash","Dogs not allowed"))

palette_color <- c("#017EB1","#F27256")

title<-paste0("Hiking with your furry friend ")

dog <- "images/dog hike/dog_allowed.png"
dog_na <- "images/dog hike/dog_not_allowed.png"
paw <- "images/dog hike/pawprint.png"



plot <- dogs_cor %>%
  mutate(features=case_when(str_detect(features,"Meadows")~"Meadows",
                                       TRUE~ features)) %>% 
  mutate(features=fct_reorder(features,correlation)) %>% 
  ggplot(aes(y = features, x = item1, fill = item1, alpha = correlation*2)) +
    geom_tile(width = 0.8, height = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = palette_color) +
     labs(
      x = '',
      y = 'Features of the hike',
      title = title,
      subtitle = 'Exploring Washington trails (wta.org) dataset to find out which factors correlate with dog allowed/not allowed feature. \nInteresting to see that hikes where dogs are allowed are mostly kid friendly where as Established campsite, waterfalls hikes usually do not allow dogs. \n\nDarker color represents positive correlation, lighter color represent negative correlation.\n',
      caption = 'Data: https://www.wta.org | Icons by Flaticon | Viz: Vaibhav Singh,'
    )+
    theme(axis.line=element_blank(),
          axis.text.x = element_blank(),
         # axis.text.y = element_blank(),
         axis.text.y = element_text(size=8, face="bold", colour = "black"), 
         axis.title.y = element_text(size=8, face="bold", colour = "Red"),
         axis.ticks.x = element_blank(),
         plot.background = element_rect(color = "#FFA9AA", fill = "#F7F6F3", size = 3),
    #  axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
    #  plot.background=element_blank(),
      plot.title = element_text(
        size = 32, 
        color = 'red',
        family = "Good boy"
      ),
      plot.subtitle = element_text(
        size = 9,family = 'IBM Plex Sans', color = '#2E383D',
      ),
      plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
      plot.caption = element_text(
        color = '#cccccc', size = 7, margin = margin(t = 6), hjust = 0.9825,
        face = 'plain'
      ),
      plot.margin = margin(20,10,10,10))+
      scale_x_discrete(expand = c(0.2,0.2),position='top')

plot_1 <-ggdraw()+
  draw_plot(plot)+
  draw_image(dog, x = 0.05, y = 0.25, scale = 0.065,hjust = 0.2)+
  draw_image(dog_na, x = 0.52, y = 0.25, scale = 0.065,hjust=0.2)+
  draw_image(paw, x = 0.36, y = 0.429, scale = 0.065,hjust=0.2)+
  draw_image(paw, x = 0.31, y = 0.429, scale = 0.065,hjust=0.2)
# 
# pimage <- axis_canvas(plot, axis = 'x') + 
#   draw_image(dog, x = 0.6,scale = 1)+
#   draw_image(dog_na, x = 1.6,  scale = 1)
#   
# plot_2 <- ggdraw(insert_xaxis_grob(plot, pimage))

  
#your most recent plot
file_path <- here(2020, "plots")
ggsave(paste0(file_path, ".pdf"), plot_1, width = 9.5, height = 6, device = cairo_pdf)
pdftools::pdf_convert(paste0(file_path, ".pdf"), filenames = paste0(file_path, ".png"), dpi = 300)

ggsave(paste0(file_path, ".jpg"), plot_1, width = 9.5, height = 6, dpi = 100,
       type = "cairo")
    
```

# Visualize

Using your processed dataset, create your unique visualization.

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save 

```
